---
title: "Assessment 3 : peer marking"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Students provide, in a concerted manner within their group, a vector of positive weights (in \%)
$$
(w_1,\ldots,w_g)\qquad \text{such that }\sum_{i=1}^gw_i=100,
$$
where $g$ is the total number of students in their group. Note that giving a weight equal to $W=100 /g$ for all students will result in all of them having the same mark.

Next, they receive a group mark $M$ (out of 100) for their group report by a lecturer.

The individual mark of the $i$th student is given by
$$
m_i=w_iM/W, \qquad i=1,\ldots,g, 
$$ 
provided all these marks are not larger than 100. Otherwise, we modify the weights and marks as follows. Let $w_{\max}$ be the largest weight among those given by the students (giving a mark $>$ 100) and $W_{\sup}=100W/M$ the weight that gives a maximal mark of 100. Let $\kappa=(W_{\sup}-W)/(w_{\max}-W)$ the ratio which permits to change the weight $w_{\max}$ to get a final mark of 100 for that student. We then change all weights $w_i$ above $W$ as follows:
$$
w_i \longleftarrow W + \kappa(w_i - W).
$$
It is straightforward to see that the largest new mark becomes $(W + \kappa(w_{\max} - W))M/W=100$.

Similarly, we change all weights $w_i$ below $W$ as follows:
$$
w_i \longleftarrow W - \kappa(W - w_i).
$$
(The sum of the new weights stay equal to 100.) We then recompute the marks with the same formula as above, namely $m_i=w_iM/W, \qquad i=1,\ldots,g$.


The corresponding R code is given below.



```{r}
compute.marks <- function(report.mark, weights) {
  # INPUT:
  #  - report.mark : mark given to the group report out of 100
  #  - weights:      vector of weights (in %) for all students in the group
  # OUTPUT:
  #  - optionnaly, vector of new weights
  #  - vector of (weighted) marks for all students in the group
  if (any(weights < 0 | weights > 100)) stop("All weights should be between 0 and 100.")
  if (abs(sum(weights) - 100) > 10 ^ (-3)) stop("The sum of weights (in %) should be 100.")
  g <- length(weights)
  W <- 100 / g
  marks <- report.mark * weights / W
  if (any(marks > 100)) {
    wmax <- weights[which.max(weights)]
    Wsup <- 100 * W / report.mark
    kappa <- (Wsup - W) / (wmax - W)
    excess.weights <- sum(weights[weights > W] - W)
    weights[weights > W] <- W + (weights[weights > W] - W) * kappa
    weights[weights < W] <- W - (W - weights[weights < W]) * kappa
    marks <- report.mark * weights / W
  }
  return(list(weights = weights, marks = marks))
}
```

Let's see an example.


```{r}
M <- report.mark <- 100
weights <-  c(25, 25, 25, 25)
g <- length(weights)
W <- 100 / g
weights2 <- weights
weights2[weights >= W] <- weights2[weights >= W] - W
weights2[weights < W] <- -W + weights2[weights < W]
par(mfrow = c(1, 2))
plot(weights2, type = "h", lwd = 3, axes = FALSE, 
     ylab = "Weights", xlab = "student", ylim = c(-20, 80))
abline(h = 0)
at <- c(-20, -10, 0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
atplus <- at + 20
atplus[3] <- "100 / g"
axis(2, at = at , labels = atplus, las = 1)
marks <- g * M * weights / 100
plot(1:g, marks, ylim = c(0, max(marks)), xlab = "student", pch = 20) ; abline(h = 100)
```


```{r}
M <- report.mark <- 100
weights <- c(25, 25, 25, 25)
( res <- compute.marks(report.mark, weights) )
sum(res$weights)
```

```{r}
weights <- c(25, 25, 25, 25)
report.mark <- 100
( res <- compute.marks(report.mark, weights) )
sum(res$weights)
```

